---
title: "Try1 Titanic Challenge"
author: "Michael Tzach"
date: "12/1/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# First attempt at submission
The first attempt at submission to Kaggle used the very basic C50 prediction model.

setting up the workspace
The training and test files are in the /Titnic directory
```{r}
workspaceDir = "/Users/michaeltzach/Developer/R/ex2/Titanic"
setwd(workspaceDir)
```


We load the training file and change the Survived and Pclass columns to be factors since they are clearly class vars
```{r}
trainingData <- read.csv("train.csv", na.string="")
trainingData$Survived = factor(trainingData$Survived)
trainingData$Pclass = factor(trainingData$Pclass)
```

We remove unwanted columns that have no influence on the probability of the person to survive.
We might in the future add the Name column and process it to get the person's title.
```{r}
trainingData = subset(trainingData, select=-c(Name, Ticket, Cabin, PassengerId))
```

We do the same for the test data so we can run it.
Before removing the passengerId data, we save it so we can use it later for creating the submission file.
```{r}
testData = read.csv("test.csv", na.string="")
#testData$Survived = factor(testData$Survived)
#testData$Pclass = factor(testData$Pclass)

testDataPassengerIds = testData$PassengerId
testData = subset(testData, select=-c(Name, Ticket, Cabin, PassengerId))
```

Divide the training set to 0.75-0.25 parts to get a cofusion matrix and test model's accuracy
```{r}
indices <- sample(1:nrow(trainingData),nrow(trainingData)*0.75)
trainingData.train = trainingData[indices,]
trainingData.test<- trainingData[-indices,]
```

Install the C50 lib and create a model. We also want to set a seed for random so we get the same results during testing
We create the model based on trainingData.train
```{r}
if(!require(C50)){
  install.packages('C50')
}
library('C50')
set.seed(123)

C50training <-C5.0(Survived ~., data=trainingData.train )
```

For the understanding of how well our model works we print some stats on how it predicted the results in the test portion of the training data
```{r}
trainingPredictions = predict(C50training, trainingData.test)
table(trainingPredictions,trainingData.test$Survived)
mean(trainingPredictions==trainingData.test$Survived)
```

We retrain the model on the complete training data set to get better results.
We create predictions on the test data set and write it to a file after binding it to the passenger ids.
```{r}
C50 <-C5.0(Survived ~., data=trainingData )
plot(C50training)
testPredictions = predict(C50training, testData)

#Create the result of the prediction
res <- cbind(PassengerId=testDataPassengerIds,Survived=as.character(testPredictions))
write.csv(res,file="try1.csv",row.names = F)
```

# Results

